---
title: "Statistical Concepts"
---

# Assignment 4

## 1. Load Library and Data

```{r}
library(dplyr)

random_vars <- readRDS("~/Documents/TUHH/Casual Data Science for Business Analytics/Causal_Data_Science_Data/random_vars.rds")
```

### The values for the age variable

```{r}
ageExpectedValue <- summarise(random_vars, mean = mean(age))
print(ageExpectedValue)
ageVariance <- var(random_vars[,1])
print(ageVariance)
ageStandardDeviation <- summarise(random_vars, sd = sd(age))
print(ageStandardDeviation)
```

### The values for the income variable

```{r}
incomeExpectedValue <- summarise(random_vars, mean = mean(income))
print(incomeExpectedValue)

random_vars %>%
  select(-income) %>%
  var()


incomeStandardDeviation <- summarise(random_vars, sd = sd(income))
print(incomeStandardDeviation)

```

## 2. Comparison
Well I believe that there's no sense to compare the standard deviations because simple the income and age aren't directly related and hence we cannot say that if someone's age is above the mean with a certain deviation that their income will increase by a certain deviation and vice versa 

## 3. Covariance and Correlation

```{r}
cov <- cov(random_vars[,1],random_vars[,2])
print(cov)

cor <- cor(random_vars[,1],random_vars[,2])
print(cor)
```
## 4. Correlation vs Covariance
Correlation is easier to interpret because it is bounded with the magnitude showing us how strong or how weak is the relationship and the sign shows us the direction. Meanwhile the covariance is value that doesn't really tell us much, in terms of the number provided.

## 5. Conditional Expected Value

1. $E[income \mid age >= 18]$  
```{r}
e1 <- summarise(random_vars[random_vars$age>=18,], mean = mean(income))
print(e1)
```
2. $E[income \mid age \in [18,65)]$
```{r}
e2 <- summarise(random_vars[random_vars$age >= 18 & random_vars$age<65,], mean = mean(income))
print(e2)
```
3. $E[income \mid age >= 65]$
```{r}
e3 <- summarise(random_vars[random_vars$age >= 65,], mean = mean(income))
print(e3)
```
