---
title: "Regression and Statistical Inference"
---

# Assignment 5

## 1. Import the data set and check dimensions
```{r}
library(tidyverse)

car_prices <- readRDS("~/Documents/TUHH/Casual Data Science for Business Analytics/Causal_Data_Science_Data/car_prices.rds")

dim(car_prices)

```

The dimensions of the data set is 188 rows and 22 coloumns 

## 2. Data glimpse and lookup
```{r}
glimpse(car_prices)
```

Here I used glimpse instead of head to help me see all the coloums and their data types. Strings are recorded as chars and numbers are double allowing decimal values.

## 3. Linear Regression

```{r}
lm_all <- lm(price ~ ., data = car_prices)
summary(lm_all)
```

From the summary we could see that the main factors relevant are: 

1. enginetype (mostly)  

2. eniginesize  

3. stroke  

4. peakrpm  

## 4. Choosing data regressor

```{r}
lm_top <- lm(price ~ enginetype +
                     enginesize +
                     stroke +
                     peakrpm,
                     data = car_prices)
summary(lm_top)
```

As we can see the smallest p-value is the one for engine size and hence im picking it to be my regressor.

```{r}
max(car_prices$enginesize)
min(car_prices$enginesize)
```

The regressor I chose is of type double and its values in this data set ranges from 61 to 326.

It has a big effect on the price since the p value is very small it denies the null hypothesis and tells that that there is a strong corellation between both factors.

```{r}
lm_summarised <- lm(price ~ enginesize, data = car_prices)
confint(lm_summarised, level = 0.95)
```

The estimate is completely positive hence the effect is statistically significant.

## 5. Adding the variable

```{r}
new_car_prices <- mutate(car_prices, seat_heating = TRUE)
lm_heat <- lm(price ~ ., data = new_car_prices)
summary(lm_heat)
```
