---
title: "Instrumental Variables"
---

# Assignment 11

## Load Data and Libraries

```{r}
library(tidyverse)
library(dagitty)
library(ggdag)
library(estimatr)

app <- readRDS("~/Documents/TUHH/Casual Data Science for Business Analytics/Causal_Data_Science_Data/rand_enc.rds")

app

```

## DAG Model

```{r}
app_model <- dagify(
  F ~ P,
  F ~ U,
  S ~ F,
  S ~ U,
  coords = list(x = c(P = 1,F = 3,U = 5.5,S = 8),
                y = c(P = 0,F = 0,U = 1.5,S = 0)),
  labels = list(P = "PopUp / Encouragement",
                F = "New Feature",
                U = "Unobserved Confounder",
                S = "Screen Time")
)

#Plot DAG model
ggdag(app_model) +
  theme_dag()+
  geom_dag_node(color = "red")+
  geom_dag_text(color = "white") +
  geom_dag_edges(edge_color = "black") +
  geom_dag_label_repel(aes(label = label))
```


## Naive Biased Estimate

```{r}
#Naive Biased Estimate

lm_biased <- lm(time_spent ~ used_ftr, data = app)
summary(lm_biased)
```

## Testing Assumptions

```{r}
app_assume <- app %>%
  filter(used_ftr == 1)

cor(app_assume$rand_enc,app_assume$time_spent)
```

### Argument 

The value of the correlation between the IV variable and the outcome given the treatment is very small at -0.0274 which is not exactly zero but very small hence it is appropriate to use it specially that we most probably have a lot of unobserved confounders that can't be all compensated/accounted for with a single IV variable.

## Computing IV estimate

```{r}
model_iv <- iv_robust(time_spent ~ used_ftr | rand_enc, data = app)
summary(model_iv)

```

### Naive vs IV

The naive estimate appears to be biased yes with a bit of upward bias as the naive estimate is higher than the IV estimate. 